A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-06 writeup/paper.tex
Minor edits

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

%
%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\includegraphics[width=\linewidth]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
%\label{lang-pie}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Survey Design}
The central task in this study was to study Mechanical Turk's bilingual population.  We accomplished this through self-reported surveys combined with a HIT to translate individual words for over 100 languages.  We evaluate the accuracy of the workers' translations against known translations.  In cases where these were not exact matches, we used a second pass monolingual HIT, which asked English speakers to evaluate if a worker-provided translation was a synonym of the known translation.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and used these to extract the 10,000 most frequent words. The resulting vocabularies served as the input to our translation HIT.

\begin{table}[h]
\scriptsize 
\begin{center}
\begin{tabular}{|p{0.95\linewidth}|}
\hline
{\sc 500k+ articles:}
Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
\hline
{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
\hline
{\sc 10k-100k articles:}
Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
\hline
{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
\end{table}%

@@

%Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
%Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems. 
%
Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.   
%
The task paid \$0.15 for the translation of 10 words.  
% 
%Assignments which had less than XXX items translated was rejected, as were workers who failed the quality control measures more than XXX\% of the time.
Each set of 10 words was independently translated by three separate workers.  5,281 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.

\paragraph{Gold standard translations} 
A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls. We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.  To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.

\paragraph{Manual evaluation of non-identical translations}
We counted all translations that exactly matched the gold standard translation as correct.  For non-exact matches we created a second-pass quality assurance HIT.  
For the evaluation task, Turkers were shown a pair of English words, one which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word. Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous.'  Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.  Non-meaning equivalents included: $<${\it assorted, minutes}$>$, and $<${\it major,} URL of image$>$.  Related items were things like $<${\it sky, clouds}$>$. Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.   3 separate Turkers judged each pair, allowing majority votes for difficult cases.

We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet \cite{miller1995wordnet}) or were known to be unrelated (randomly chosen from a corpus). 
%We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
Automating the evaluation in this way allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique word pairs).  These were completed by an additional 1,006 workers.  Each of these assignments included 10 word pairs and paid \$0.10.

@@

>>>>

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

%
%%%%%%%%%%%%%%%% NAT LANG PIE %%%%%%%%%%%
%\begin{figure}[h]
%\centering
%\includegraphics[width=\linewidth]{figures/natlang-pie}
%\caption{Self-reported native language of 3,154 bilingual Turkers.  Not shown are the languages of 243 Turkers who reported two native languages, 83 who reported $\geq$3 native languages, and 1.801 who failed to answer the language survey component of our translation HITs.}
%\label{lang-pie}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Survey Design}
The central task in this study was to investigate Mechanical Turk's bilingual population.  We accomplished this through self-reported surveys combined with a HIT to translate individual words for over 100 languages.  We evaluate the accuracy of the workers' translations against known translations.  In cases where these were not exact matches, we used a second pass monolingual HIT, which asked English speakers to evaluate if a worker-provided translation was a synonym of the known translation.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} and then selected an additional 19 languages low resource languages with $<$10,000 articles, giving a total of 119 languages (Table \ref{wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them. The resulting vocabularies served as the input to our translation HIT.

% Todo: sort by language code, rebalance the bottom set to have 19 languages in it.
\begin{table}[h]
\scriptsize 
\begin{center}
\begin{tabular}{|p{0.95\linewidth}|}
\hline
{\sc 500k+ articles:}
Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
\hline
{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
\hline
{\sc 10k-100k articles:}
Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
\hline
{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
\end{table}%

@@

%Our experiments consist of two task types: a translation HIT and an evaluation HIT. 
%Examples of the interface for each are shown in figures \ref{tranhit} and \ref{synhit}.  
For the translation task, we asked Turkers to translate individual words.  We showed each word in the context of three sentences that were drawn from Wikipedia.  
Turkers were allowed to mark that they were unable to translate a word. Each task contained 10 words, 8 of which were words with unknown translations, and the other two of which were quality control words with known translations.   
We gave special instruction for translating names of people and places, giving examples of how to handle `Barack Obama' and `Australia' using their interlanguage links. For languages with non-Latin alphabets, names were transliterated.

%
The task paid \$0.15 for the translation of 10 words.  
% 
%Assignments which had less than XXX items translated was rejected, as were workers who failed the quality control measures more than XXX\% of the time.
Each set of 10 words was independently translated by three separate workers.  5,281 workers completed 308,079 translations assignments, totaling more than 3 million words, over a period of three and a half months.

\paragraph{Gold standard translations} 
A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls. We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign articles title.  To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.

\paragraph{Manual evaluation of non-identical translations}
We counted all translations that exactly matched the gold standard translation as correct.  For non-exact matches we created a second-pass quality assurance HIT.  
Turkers were shown a pair of English words, one of which was a Turker's translation of the foreign word used for quality control, and the other was the gold-standard translation the foreign word. Evaluators were asked whether the two words had the same meaning, and chose between three answers: `Yes', `No', or `Related but not synonymous.'  Examples of meaning equivalent pairs include: $<${\it petroglyphs, rock paintings}$>$, $<${\it demo, show}$>$ and  $<${\it loam, loam: soil rich in decaying matter}$>$.  Non-meaning equivalents included: $<${\it assorted, minutes}$>$, and $<${\it major,} URL of image$>$.  Related items were things like $<${\it sky, clouds}$>$. Misspellings like $<${\it lactation, lactiation} $>$ were judged to have same meaning, and were marked as misspelled.   3 separate Turkers judged each pair, allowing majority votes for difficult cases.

We checked Turkers who were working on this task by embedding pairs word which were either known to be synonyms (drawn from WordNet) or  unrelated (randomly chosen from a corpus). 
%We drew known synonyms from WordNet, and non-synonyms by pairing random words from a corpus of English (including them after they were determined to be unrelated according to WordNet).
Automating approval/rejections for the second-pass evaluation allowed the whole pipeline to be run automatically.  Caching judgments meant that we ultimately needed only 
20,955 synonym tasks to judge all of the submitted translations (a total of 55,880 unique non-matching word pairs).  These were completed by an additional 1,006 workers.  Each of these assignments included 10 word pairs and paid \$0.10.

@@

\paragraph{Use of machine translation}
Following \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we rendered the words and sentences as images to reduce the ability of workers to cheat by copying-and-pasting into online MT systems.  This strategy does not prevent workers from typing the words into a MT system, if they understand the language's script.
%
